A Machine Profile Summary

### 2022-01-18 MachineSummary/MachineSummary.Rmd
minor edit

An important tool for acquiring machine information is the CRAN package
`benchmarkme` (@benchmarkme). We found a minor bug in the `get_ram()`
function of this package for some Windows 10 versions which is now 
corrected (??check it is uploaded). ??Do we wish to comment on the
"GB" issue?

>>>>

An important tool for acquiring machine information is the CRAN package
`benchmarkme` (@benchmarkme). We found a minor bug in the `get_ram()`
function of this package for some Windows 10 versions which is now 
corrected on https://github.com/csgillespie/benchmarkme, but at the 
time of writing is not yet on the CRAN repository. ??Do we wish to comment on the
"GB" issue?
